---
title             : 'The many meanings of "um": \newline Children draw rich, contextual social inferences after hearing speech disfluencies'
shorttitle        : "Social Inferences from Speech Disfluencies"

author: 
  - name          : "Benjamin C. Morris"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, University of Chicago, 5848 S University Ave, Chicago, IL 60637"
    email         : "benmorris@uchicago.edu"
  - name          : "Daniel Yurovsky"
    affiliation   : "1,2"
    corresponding : no    # Define only one corresponding author
  - name          : "Alex Shaw"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author


affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "Carnegie Mellon University"

author_note: >

abstract: >
  Successfully navigating the social world requires figuring out what others know, like, want, and more. Timing and delay in someone's actions hold rich, nuanced information about their underlying mental states. In language, delays are commonly expressed as disfluencies (e.g., the filled pauses "uh" and "um"). Adults use silent pauses to infer speaker desires [@roberts2011] and disfluencies to infer speaker knowledge [@brennan1995]. Across three studies, we explore at what point in development children (aged 4- to 9-years-old) use speech disfluences to make rich social inferences about the mental states of others. In Experiments 1a and 1b (n = 44), we present pilot evidence that children infer that a speaker who answers a question accurately, but disfluently is less knowledgable than an accurate and fluent speaker; however, they make no such inference when the speakers express ignorance instead (e.g., I don't know). In Experiment 2 (n = 101), we replicate these results in a larger, pre-registered study, and show that even 4-5 year old children make these inferences. In Experiment 3 (n = 56), we show that these effects generalize to other social inferences-- when discussing preferences, children age 6 and older infer a disfluent speaker has a weaker preference than a fluent speaker. Additionally, across Experiments 2 and 3, we see evidence suggesting that children's ability to infer knowlege from disfluencies may emerge earlier than their ability to infer preferences. Overall, this work demonstrates that children can make a range social inferences based on speech disfluencies, flexibly recognizing that disfluencies can mean different things in different contexts.
  
keywords          : "communication, speech disfluency, mental-state inference, hesitation, uncertainty, processing time"
wordcount         : "X"

bibliography      : ["umm.bib"]

header-includes:
  - \usepackage{xcolor}

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

---


```{r load-packages, warning = F}
library(papaja)
library(feather)
library(here)
library(lme4)
library(lmerTest)
library(png)
library(boot)
library(broom)
library(broom.mixed)
library(ggthemes)
library(tidyverse)
library(tidyboot)
library(glue)
library(xtable)

knitr::opts_chunk$set(fig.pos = 'tb', echo = FALSE, cache = TRUE, 
                      warning = FALSE, message = FALSE, 
                      sanitize = TRUE, fig.path='figs/', fig.width = 3,
                      fig.height = 3)

theme_set(theme_classic(base_size = 12) + theme(legend.position = "none")) 
options(digits = 3, dplyr.summarise.inform = FALSE)
set.seed(42)
```

\newcommand{\E}[1]{\mathbb{E}\left[ #1 \right]}

```{r make-text-vars}
make_text_vars <- function(df, term_name, term_filter = NULL) {
  if(!is.null(term_filter)) {
    filtered_df <- df %>%
      filter(term == term_filter) 
  } else{
    filtered_df <- df
  }
    
  walk(c("estimate", "statistic", "p.value"), 
      ~assign(glue("{term_name}_{.x}"), 
              filtered_df %>% pull(!!.x), 
         envir = globalenv()))
}
```

<!-- 9. Might want to add N's for condition/age break down to figures. -->

Imagine you ask someone on the street, "Where is the nearest train station?" and they reply "It’s um... that way." While plausibly correct, the stranger's reply is slow and marked, indicating uncertainty about accuracy of their statement.  Despite getting a relevant answer, you yourself may still feel uncertain, perhaps choosing to confirm the direction by consulting another stranger or checking your smartphone. In this way, adults can use disfluencies to make inferences about the inner workings of a speaker's mind, which is an important social cognitive skill that can shape how they learn from and evaluate others. *How* something is said may be as meaningful as *what* is said. When in development can children use disfluencies to make inferences about others' mental states? In three studies with children 4 to 9 years old, we explore this question.

<!-- In the example above, the stranger seems uncertain because they spoke disfluently, pausing in the middle of their utterance. When it comes to how something should be said, language is profoundly structured by an expectation of timeliness. Conversations across at least 10 typologically diverse languages are structured around remarkably short and consistent silences between speakers [@stivers2009]. Speakers of a given language show nuanced judgments for what consitutes a reasonable, or unreasonable, delay during a conversation, though the duration of that acceptable delay varies across languages [@stivers2009]. Thus, conversation is powerfully structured to avoid delays when possible.  -->

Producing language in a timely manner may often conflict with demands on processing, memory, and many other factors liable to cause delays. When such delays are unavoidable, speakers may mark them with disfluencies (e.g., filled pauses "uh" and "um"). Conversation is rife with these small disruptions; some data sources estimate that 6 disfluencies occur every 100 words in adult conversations [@foxtree1995; @shriberg1996]. Disfluencies allow speakers to hold the conversational floor while having planning difficulties or searching for an answer [@clark2002; @smith1993]. As a result, disfluencies may signal something to the listener about the cognitive process that generated them.

Children likely have abundant and systematic experience hearing disfluencies in the language around them [@shriberg1996; @kidd2011]. Young children also have first-hand experience with disfluencies in their own productions-- prevalent from at least age 2 [@casillas2014]. 22-month-old infants distinguish between fluent and disfluent adult-directed speech, suggesting that children are sensitive to disfluencies in the second year of life [@soderstrom2007]. 

Still more impressive, by their second birthday, toddlers are able to monitor these cues online and predict that a disfluent speaker will likely refer to a novel object that is new to the discourse, rather than a familiar one that has already been discussed [@kidd2011].  Later in development this predicition may be tied to a speaker's knonwledge: 3 1/2-year-olds make the same prediction when pre-trained on a reliable speaker, but show no such prediction when pre-trained on a forgetful speaker who fails to remember the names familiar objects during training [@orena2015]. From an early age, children reason about speech disfluencies and use them to guide referential inferences.

While disfluencies are clearly powerful cues for predicting language, disfluencies reflect general processing delays and thus could underwrite broad inferences about the processes going on in other people's minds. Indeed, there is some evidence that adult listeners speech fluency to draw a range of social inferences. When responding to requests (e.g., "Can you give me a ride?"), a speaker who pauses before responding is seen as less willing to accept the request [@roberts2006; @roberts2011]. Similarly, when agreeing with another's past statement (e.g., "The flyers look good."), delays are seen as indicating less agreement [@roberts2011]. These speaker judements are even titrated by the degree of delay-- the longer the delay, the less willing a speaker seems [@roberts2011].

Adults also use disfluencies, including filled pauses (e.g., "um"), to infer a speaker's knowledge. When a speaker answers a trivia question accurately, but disfluently, adult listeners infer that person is less knowledgable about that information, compared with a speaker who gives accurate and speedy answer [@brennan1995]. Interestingly, there is even some evidence that when speakers produce non-answers (e.g., "I don't know" or "I can't remember"), disfluency leads adults to infer greater knowledgeability-- perhaps assuming the disfluency arose from attempting to retrieve the answer before failing [@brennan1995]. These results suggest adults may be reasoning about the underlying mental process that delays speech in powerfully flexible ways. Holding constant what a speaker says, the speed and fluency with which a speaker says it licenses broad, contextual inferences about their mental states.

While no work has directly examined the development of these inferences, a small literature examines children abilities to reason about timing more broadly. In the physical domain, young children believe an agent who succesfully builds a tower faster than another agent building the same tower is better at building-- though when the difficulty of the tower is also varied children have more trouble inferring relative competence [@leonard2019]. Relatedly, children may use the speed a character solves puzzles in a story to infer competence, at least in some contexts [@heyman2006]. By age 7, children seem to use response time on a difficult problem to infer the likely underlying mental process, such that a quick answer is judged as a retrieved memory and a longer response time is judged as a in-the-moment solution [@richardson2020]. Timing is an everyday force that even young children are likely very familiar with, and these studies suggest it may be a useful cue in the development of social reasoning.

<!-- COMMENT FROM AS 4. could probably use a tiny paragraph that talks a bit more about why this is an interesting kid question. Don't think it's essential, but might be nice. This could both motivate the question and give people the broader framework of what we are trying to show. -->

In the present studies, we test how and when young children use speech disfluencies to draw social inferences about a speaker's knowledge and preferences across a range of conversation contexts. We show that children infer an accurate, but disfluent speaker is less knowledgable (Experiments 1a and 2a), but only in certain conversational contexts (Experiments 1b and 2b). Then in a new conversational context, we demonstrate that children are similarly able to use disfluency to infer a speaker's relative preference (Experiment 3). See Table \ref{tab:exp-table} for an outline of each experiment's design. Ongoing work further examines the richness of children's preference inferences, such as inferring relative dispreference.

```{r exp-table, results="asis", tab.env = "table", tab.align="center", tab.cap = "Table containing the desgin and utterance stimuli for each experiment."}
tab <- tibble(Experiment = c("Exp 1a", 
                            "Exp 1b",
                            "Exp 2a",
                            "Exp 2b",
                            "Exp 3"),
              Population = c("Children", 
                      "Children", 
                      "Children", 
                      "Adults", 
                      "Children"),
              Method = c("In-Person", 
                      "In-Person", 
                      "In-Person", 
                      "Online", 
                      "Online"),
              Condition = c("Labelling", 
                      "Ignorance", 
                      "Labelling & \n Ignorance", 
                      "Labelling & \n Ignorance", 
                      "Preference"),
              `Fluent Utterance` = c('"This one is a cat."', 
                      '"I don\'t know."', 
                      '"This one is a tiger."', 
                      '"This one is a tiger."', 
                      '"The tiger is my favorite."'),
              `Disfluent Utterance` = c('"This one is a uh... cat."', 
                      '"Uh... I don\'t know."', 
                      '"This one is a uh... tiger."', 
                      '"This one is a uh... tiger."', 
                      '"Um... the tiger is my favorite."'),
              )


print(xtable(tab, display = c("s", "s", "s", "d", "d", "d", "f")),
      type = "latex", comment = F, table.placement = "tb",
      include.rownames = FALSE, size="\\fontsize{9pt}{8pt}\\selectfont")
```


```{r child = "sections/knowledge_pilot.Rmd"}
```

```{r child = "sections/knowledge_experiment.Rmd"}
```

```{r child = "sections/preference_experiment.Rmd"}
```

# General Discussion

Across 3 studies, children draw inferences about another agent's mental states based solely on the disfluencies in their speech, and these inferences are flexible and context-sensitive. We see consistent evidence that even young children infer that a disfluent speaker might be less knowledgeable. By age 6, children similarly use disfluencies to infer the relative preferences of a speaker. In sum, these findings suggest that disfluencies may serve as powerful cues to a speaker's mental processes, with broad applications.

These studies add to the rich literature on children's ability to infer knowledgeability and engage in selective social learning [e.g., @koenig2005]. In our studies, children make selective competence judgements, even while holding speaker accuracy constant. These results parallel recent demonstrations that young children are able to use accuracy-irrelevant information in selective social learning paradigms [@aboody2018; @corriveau2016]. In our study, 4-5 year old children (as young as we tested) made these contextual knowledge inferences at rates similar to adults.

We see preliminary evidence that children's ability to draw inferences about knowledge emerges earlier in development than preference in this task. Across both Experiment 2 and 3, children age 4-5 seem to infer a disfluent speaker might be less knowledgable, but do not extend this inference to the preference domain in Experiment 3 until age 6-7. These results are unlikely to be explained by difficulty following the task, as we see this pattern even looking within-subjects in Experiment 3. That is, the same 4-5 year old children make no systematic preference inference in trial 1, but do infer knowledge on trial 2. These preliminary results present the intriguing possiblity that children may more easily connect fluency and knowledge, compared with fluency and preference. Future work is needed to test the robustness of this developmental change.

While adults derive a range of social inferences based on speech timing and disfluency [@brennan1995; roberts2011], these inferences are likely built on underlying general inferences about processing delays and their richness comes from contextualized interpretation. That is, these delays often acquire social meaning only after integrating information from the conversational context-- such as inferring that someone who says "sure" slowly is less willing to go along with previous speaker's request. It is possible that the preference inference in our experiments required more contextual information than the knowledge inference and was more difficult for young children as a result.

Children are not merely responding heuristically to the percieved confidence of a speaker, but instead flexibly and contextually employing these inferences. Children as young as 2 are sensitive to an agent's confidence (e.g., facial expression, gesture, etc.) and selectively imitate more confident agents [@birch2010]. Our results cannot be explained by tracking confidence, as a confidence account should predict systematic choices in the ignorance conditions where children and adults show no speaker preference. We also see that children will select the disfluent speaker as having a stronger dispreference, though this effect is difficult to interpret in these data.

<!-- 15. Lmight be worth adding one more paragraph on cool future work in this area to stake out your turf a bit more. -->

Disfluencies are powerful cues for inference-- available in-the-moment and informative regardless of whether the child has the relevant knowledge to judge a speaker’s statement While these cues are doubtless helpful in language processing, this work extends such findings to suggest that these cues additionally serve a range of social inferences in early childhood. Disfluencies track processing difficulties, and thus can provide a useful window into an agent's mental processes, beyond the content of what is said. As young children learn about the social world, tracking speech disfluencies and processing delays broadly may provide a rich dataset for drawing social inferences.

# Acknowledgement

The authors are grateful to Cassidy Wilson and Madison Collins for their assistance in data collection. 

\newpage

# References


\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
