# Experiment 3

Our account holds that disfluencies can be interpreted by listeners as domain general signs of processing time or conflict. As such, disfluencies should generate inferences in a variety of domains, beyond knowledgeablility. We next ask how children use speech disfluencies to infer an agent's preferences and dispreferences.

In Experiment 3, we changed the question under discussion so that each character is asked which of the two animals they like the best. Disfluency here may indicate a speaker is experiencing conflict between the two options, delaying their response time, while speed may indicate a strong and decisive preference (similar to the degree of agreement inference made by adults in Roberts et al., 2011). When two speakers both state the same preference, but one does so disfluently, we predicted that children would infer they had a relatively weaker preference. 

We further expected that this situation might license an additional inference about dispreference. With two options on the table, delay in naming one's favorite may reflect difficulty due to relatively split preferences. Consistent with this reasoning, we asked children to report who likes the unlabelled animal more (i.e. the dispreferred item), and we expected that children would infer the disfluent speaker may have a relatively stronger preference for this item. We hypothesized that this dispreference inference might be difficult for our youngest children, based on some evidence that children as young as infancy seem better able to represent preference than dispreference (Feiman, Carey, & Cushman, 2015). 

<!-- 14. The really subtle knowledge vs. preference condition kind of comes out of no where in Study 3. I think I'd preview this more in intro to Study 3. Maybe going through the different predictions in turn. Our first question was can they do this with preferences and do children do preferences at the same age as knowledge? NEW PARAGRAPH. Can they also make this other inference about the non-target object? NEW PARAGRAPH Is this inference about the non-target target object selective to preferences? -->

Data for Experiment 3 were conducted remotely over Zoom, as described more below. To establish that our paradigm sucessfully translated to remote testing, we also included an additonal knowledge trial in Experiment 3, attempting to replicate our findings from Experiment 2a. 


```{r e3}
umm_pref <- read_csv(here("data/umm_pref_clean.csv"))

umm_pref$question <- factor(umm_pref$question, levels = c("pref", "basketball", "dispref", "know_label", "soccer", "know_unlabel"), ordered = T)
```

## Methods

### Participants

We pre-registered a planned sample of 60 children to run in Experiment 3. Again, we planned to collect data from 20 children in each of 3 pre-deterimend age-groups: 4-5 years-old, 6-7 years-old, and 8-9 years-old. These data were collected online via Zoom with a live experimentor. Particpanting families were largely recruited via a participant database of Chicagoland families who have previously participated in in-person research studies. These data are still being collected, with a current sample of 56 children (16 children ages 4-5, 20 children ages 6-7, and 20 children ages 8-9). 

### Procedure

In Experiment 3, the general procedure was largely matched to the previous experiments. We made some changes to facillitate the shift to remote data collection, such as changing the response format (described below). The central change of interest was to shift the question under discussion.

#### Preference Trial

In Experiment 3, two characters were introduced one at a time, and each character was given an identifiable color by which they are referred (e.g., "the blue person"). This change facillitated children's ability to respond verbally when asked to select a character, rather than pointing to a character which is difficult to capture in remote testing. In Experiment 3, each speaker entered the scene independently, and was alone when asked a question. Viewing the tiger and the zebra, each speaker was asked, "Which of these animals is your favorite? Which one do you like the best?" Both speakers independently stated a preference for the same animal, but one did so disfluently, saying e.g., "Um... the tiger is my favorite." At the end of the trial both speakers were then brought back and children were reminded what each speaker said. This ensured that both speakers were onscreen when the target questions were asked. Across participants, we counterbalanced whether the first or second speaker was the disfluent speaker, and which animal was preferred.

Children were then asked three questions: a preference question: "Who do you think likes the tiger more?", a distractor question: "Who do you think is better at playing basketball?", and a dispreference question: "Who do you think likes the zebra more?" The order of the preference and dispreference questions was counterbalanced across participants. The distractor question was always asked second to ensure children were not merely switching responses across questions. Children completed one preference trial.

#### Knowledge Trial

After switching to remote testing due to the onset of the Covid-19 pandemic, we wanted to ensure that our paradigm successfully translated to online testing from in-person adminsitration. As an initial check, we included an additional trial always after the key preference trial described above. We made a few additional alterations to our paradigm, thus this additional trial cannot serve as a true replication, but to the extent that we see similar results, it may suggest our online task is an effective replacement of in-person testing.

The Knolwedge trial was structured exactly like the preference trial described above. As in Experiments 1 and 2, the characters in the story were asked, "What is this animal called?" but both were asked about the same animal and respond while alone. Each speaker labelled the animal accurately, but one did so disfluently (e.g., saying "This one is a... um... pig."). Then, both speakers were shown and children were reminded who said what. 

Children were then asked three questions: a labelled knowledge question: "Who do you think knows more about [pigs]?", a distractor question: "Who do you think is better at playing soccer?", and an unlabelled knowledge question: "Who do you think knos more about [cows]?" The order of the labelled and unlabelled knowledge questions was counterbalanced across participants. The distractor question was always asked second to ensure children were not merely switching responses across questions. Children completed one knowledge trial.

```{r pref-results, fig.height = 4, fig.width = 6, fig.cap="Preference trial results from Experiment 3 with bootstrapped 95% confidence intervals (black lines). The dashed line indicates chance responding."}
umm_pref %>%
  filter(Trial == "Trial 1") %>%
  # count(question, speaker, Age_Binned) %>%
  group_by(question, Age_Binned) %>%
  # mutate(prop = n / sum(n)) %>%
  # filter(speaker == "Fluent") %>%
  tidyboot_mean(speaker_bin) %>%
  ggplot(aes(x = question, y = empirical_stat)) +
  geom_bar(stat='identity', fill = "maroon") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_hline(yintercept = .5, linetype="dashed", color="black") +
  facet_grid(. ~ Age_Binned) +
  theme(axis.text.x = element_text(angle = 10, hjust=.5)) +
  ylab("Proportion of Children Selecting \n the Fluent Speaker") +
  ggtitle("Trial 1: Preference Inferences")
```

```{r know-results, fig.height = 4, fig.width = 6, fig.cap="Knowledge trial results from Experiment 3 with bootstrapped 95% confidence intervals (black lines). The dashed line indicates chance responding."}
umm_pref %>%
  filter(Trial == "Trial 2") %>%
  # count(question, speaker, Age_Binned) %>%
  group_by(question, Age_Binned) %>%
  tidyboot_mean(speaker_bin) %>%
  # mutate(prop = n / sum(n)) %>%
  # filter(speaker == "Fluent") %>%
  ggplot(aes(x = question, y = empirical_stat)) +
  geom_bar(stat = 'identity', fill = "steelblue") +
  geom_linerange(aes(ymin=ci_lower, ymax=ci_upper)) +
  geom_hline(yintercept = .5, linetype = "dashed", color = "black") +
  facet_grid(.~Age_Binned) +
  theme(axis.text.x = element_text(angle = 10, hjust=.5)) +
  xlab("Question") +
  ylab("Proportion of Children Selecting \n the Fluent Speaker") +
  ggtitle("Trial 2: Knowledge Inferences")
```



## Results

Note that data colleciton remains ongoing for the youngest age group (4-5 year-olds, current n = 16/20) in Experiment 3, so we will only report overall effects at this time.

### Preference.

We first analyze children's judgements from trial 1 (the preference trial). When asked which speaker likes the preferred animal more, children were signficantly more likely to select the fluent speaker. When asked which speaker likes the dispreferred animal more, children were signficantly less likely to select the fluent speaker. When asked the distractor question, children showed no robust preference for one speaker over another.

### Knowledge.

Next, we analyze children's judgements from trial 2 (the knowledge trial). We see preliminary evidence that the updated paradigm administered over Zoom provides a conceptual replication of our in-person results from Experiment 2. Asked which speaker knows more about the labelled animal species, children were significantly more likely to select the fluent speaker than the disfluent speaker. This suggests that our paradigm successfully adapted to the Zoom administration. Additionally, when asked the distractor question, children showed no robust preference for one speaker over another.

We expected that when asked who knows more about the unlabelled animal, children would be at chance or even favor the fluent speaker. However, children were signficantly more likely to select the disfluent speaker as more knowledgeable about the unlabelled animal. We return to this result below.

## Discussion

Overall, we find support for the idea that children use disfluencies not just to make knowledge inferences, but to make preference inferences as well, consistent with an account where disfluencies serve to signal general delays in processing with contextual intepretation. 

While our data collection is still ongoing with the youngest age-group (4-5 year-olds), the current data suggest these youngest children may not be drawing reliable preference inferences. This would be an interesting contrast to our findings from Experiment 2a, which are replicated here, that 4-5 year-olds are able to infer knoweldgeability in a closley matched task. One interesting possiblity is that connection between disfluency and knowledge emerges before it is connected to other domains like preference, at least in this task.

The data on children's inference of dispreference are more difficult to interpret. While children do reliably select the disfluent speaker as having a stronger preference for the unlabelled object as we  predicted, we see a similar, unpredicted pattern for children's knowledge inferences about the unlabelled animal. That is, while children made domain-wide competence inferences in Experiment 2a, and reliably report that the fluent speaker knows more about the animal they mentioned, they seem to make the opposite inference when asked about another, unlabelled animal. These data make the dispreference measure difficult to interpret, since this inference may be driven by order effects or task demands. In this experiment, the preference trial was our focus, thus the knowledge trial was always completed subsequently. It is possible that the pattern of responses evident in trial 1 carried over to trial 2 and affected children's knowledge judgements as well. Ongoing work examines the effect of order on this inference.  


